---
title: "TidyCensus"
output: html_document
date: '2022-12-07'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
install.packages(c("tidycensus", "tidyverse"))
install.packages("acs")
install.packages("DT")

```

```{r}
library(tidycensus)
library(tidyverse)
library(acs)

census_api_key("5e3ba95b31e60d07bccd54c85ace6675826e6e6f")

acs::api.key.install(key="5e3ba95b31e60d07bccd54c85ace6675826e6e6f")
```


```{r}
## Testing 

age10 <- get_decennial(geography = "county", state="MS",
                       variables = "P013001", 
                       year = 2010)

#age10

v19 <- load_variables(2019, "acs5", cache=TRUE)
#View(v19)

	
#B17010B_002
tidypov <- get_acs(geography = "county", state="MS",
                       variables = "B17010B_002", 
                       year = 2019)
#tidypov

tidypov <- get_acs(geography = "county", state="MS",
                       table = "B17001", 
                       year = 2019, output="wide")
#tidypov

MS_geo <- geo.make(state = "MS", county = "*")
pov2 <- acs.fetch(endyear=2019, span = 5, geography = MS_geo, table.number="B17001", col.names = "pretty")

#pov2

#View(tidypov)
#dflist[[3]]

#(dflist[[3]]$`Income in the past 12 months below poverty level:`/
#dflist[[3]]$Total)* 100

tidypov

```


```{r}
year <- 2020
v19 <- load_variables(year, "acs5", cache=TRUE)
subjectvars <-  load_variables(year, "acs5/subject", cache=TRUE)

getdata <- function(tablename, racetablename=tablename, returnvars=FALSE, raceavailable=TRUE, subject=FALSE) {
  if (subject) {
    subjectvars <- data.frame(filter(subjectvars, grepl(paste0(tablename,"|",racetablename), name)))
    vars <-data.frame(filter(v19, grepl(paste0(tablename,"|",racetablename), name)))
  }
  else{
    vars <- data.frame(filter(v19, grepl(paste0(tablename,"|",racetablename), name)))
  }
  
  df_all <- get_acs(geography = "county", state="MS",
                         table = tablename, 
                         year = year, output="wide")
  if (raceavailable){
    df_b <- get_acs(geography = "county", state="MS",
                           table = paste0(racetablename, "B"), 
                           year = year, output="wide")
    df_w <- get_acs(geography = "county", state="MS",
                           table = paste0(racetablename,"A"), 
                           year = year, output="wide")
    df_list <- list(df_all, df_b, df_w)
    fulldf <- df_list %>% reduce(full_join, by='GEOID')
  }
  else {
    fulldf <- df_all
  }
  tidyfulldf <- as.data.frame(fulldf)
  htmlwidgets::saveWidget(DT::datatable(vars), "vars.html")
  if (subject) {
    htmlwidgets::saveWidget(DT::datatable(subjectvars), "subjectvars.html")
  }
  if (returnvars){
    return(list(tidyfulldf, vars))
  }
  else {
    return(tidyfulldf)
  }
}

```

```{r}
tidypovdf <- getdata("B17001")
allvars <- tidypovdf %>% select(GEOID, NAME)
```

#Poverty
totalpop B17001_001, ibp: all B17001_002, ibp male B17001_003, ibp female B17001_017
above B17001_031, above male B17001_032, above female B17001_046
for white: add A after B17001, B for black

```{r}
alldems <- c("_A_A", "_A_B", "_A_W", "_M_A", "_M_B", "_M_W", "_F_A", "_F_B", "_F_W")
# IBP, IAP, 
#denominator for some of them is adding up below poverty and above poverty values to get total
tidypovdf <- tidypovdf %>% mutate( 
              IBP_A_A = 100 * B17001_002E/ B17001_001E,
              IBP_A_B = 100 *B17001B_002E/B17001B_001E,
              IBP_A_W = 100 *B17001A_002E/B17001A_001E,
              IBP_M_A = 100 *B17001_003E/ (B17001_003E+B17001_032E),
              IBP_M_B = 100 *B17001B_003E/ (B17001B_003E+B17001B_032E),
              IBP_M_W = 100 *B17001A_003E/ (B17001A_003E+B17001A_032E),
              IBP_F_A = 100 *B17001_017E/ (B17001_017E+B17001_046E),
              IBP_F_B = 100 *B17001B_017E/ (B17001B_017E+B17001B_046E),
              IBP_F_W = 100 *B17001A_017E/ (B17001A_017E+B17001A_046E),
              IAP_A_A = 100 - IBP_A_A,
              IAP_A_B = 100 - IBP_A_B,
              IAP_A_W = 100 - IBP_A_W,
              IAP_M_A = 100 - IBP_M_A,
              IAP_M_B = 100 - IBP_M_B,
              IAP_M_W = 100 - IBP_M_W,
              IAP_F_A = 100 - IBP_F_A,
              IAP_F_B = 100 - IBP_F_B,
              IAP_F_W = 100 - IBP_F_W,
              )
allvars <- full_join(allvars, tidypovdf %>% select(GEOID, IBP_A_A, IBP_A_B, IBP_A_W, IBP_M_A, IBP_M_B, IBP_M_W, IBP_F_A, IBP_F_B, IBP_F_W), by="GEOID")
#allvars <- full_join(allvars, tidypovdf %>% select(matches("IAP|GEOID")), by="GEOID")
```

#Median Earnings
B20017_001 general, _002 male general, _003 male ft, 004 male not ft
005 female general, 006 female ft, 007 female not ft
- no race for ft and non ft (so no A_B, A_W)
- also no everyone for ft and nonft, app crashes currently (A_A)
This is really just a matter of renaming variables to fit our current structure
```{r}
tidymedearningsdf <- getdata("B20017")

tidymedearningsdf <- tidymedearningsdf %>% rename( 
  Median_Earnings_A_A = B20017_001E,
  Median_Earnings_A_B = B20017B_001E, 
  Median_Earnings_A_W = B20017A_001E,
  Median_Earnings_M_A = B20017_002E,
  Median_Earnings_M_B = B20017B_002E,
  Median_Earnings_M_W = B20017A_002E,
  Median_Earnings_F_A = B20017_005E,
  Median_Earnings_F_B = B20017B_005E,
  Median_Earnings_F_W = B20017A_005E,
  FT_Median_Earnings_M_A = B20017_003E,
  FT_Median_Earnings_M_B = B20017B_003E,
  FT_Median_Earnings_M_W = B20017A_003E,
  FT_Median_Earnings_F_A = B20017_006E,
  FT_Median_Earnings_F_B = B20017B_006E,
  FT_Median_Earnings_F_W = B20017A_006E,
  Other_Median_Earnings_M_A = B20017_004E,
  Other_Median_Earnings_M_B = B20017B_004E,
  Other_Median_Earnings_M_W = B20017A_004E,
  Other_Median_Earnings_F_A = B20017_007E,
  Other_Median_Earnings_F_B = B20017B_007E,
  Other_Median_Earnings_F_W = B20017A_007E
)

tidymedearningsdf <- tidymedearningsdf %>% mutate(
  GenderWageGap_A_A = FT_Median_Earnings_F_A, FT_Median_Earnings_M_A)

allvars <- full_join(allvars, tidymedearningsdf %>% select(matches("_A|_B|_W|GEOID")), by="GEOID")
```

##Education
Less_than_high_school_diploma c...003 / 
A_B, A_W, M_B, M_W, F_B, F_W, 
```{r}
tidyedudf <- getdata("B15002", "C15002")

lessthanhs_m_vars <- paste0("B15002_00", 3:9, "E")
lessthanhs_m_vars <- append(lessthanhs_m_vars, "B15002_010E")
lessthanhs_f_vars <- paste0("B15002_0", 20:27, "E")
combined <- append(lessthanhs_m_vars, lessthanhs_f_vars)

tidyedudf <- tidyedudf %>% mutate(
  #male less than + female less than all over total population 25 years and over
  Less_than_high_school_diploma_A_B = (100 * (C15002B_003E + C15002B_008E))/C15002B_001E,
  Less_than_high_school_diploma_A_W = (100 * (C15002A_003E + C15002A_008E))/C15002A_001E,
  Less_than_high_school_diploma_M_B = (100 * C15002B_003E)/C15002B_002E,
  Less_than_high_school_diploma_M_W = (100 * C15002A_003E)/C15002A_002E,
  Less_than_high_school_diploma_F_B = (100 * C15002B_008E)/C15002B_007E,
  Less_than_high_school_diploma_F_W = (100 * C15002A_008E)/C15002A_007E,
  "High_school_graduate_(includes_equivalency)_A_B" = (100 * (C15002B_004E + C15002B_009E))/C15002B_001E,
  "High_school_graduate_(includes_equivalency)_A_W" = (100 * (C15002A_004E + C15002A_009E))/C15002A_001E,
  "High_school_graduate_(includes_equivalency)_M_B" = (100 * C15002B_004E)/C15002B_002E,
  "High_school_graduate_(includes_equivalency)_M_W" = (100 * C15002A_004E)/C15002A_002E,
  "High_school_graduate_(includes_equivalency)_F_B" = (100 * C15002B_009E)/C15002B_007E,
  "High_school_graduate_(includes_equivalency)_F_W" = (100 * C15002A_009E)/C15002A_007E,
  Some_college_or_associates_degree_A_B = (100 * (C15002B_005E + C15002B_010E))/C15002B_001E,
  Some_college_or_associates_degree_A_W = (100 * (C15002A_005E + C15002A_010E))/C15002A_001E,
  Some_college_or_associates_degree_M_B = (100 * C15002B_005E)/C15002B_002E,
  Some_college_or_associates_degree_M_W = (100 * C15002A_005E)/C15002A_002E,
  Some_college_or_associates_degree_F_B = (100 * C15002B_010E)/C15002B_007E,
  Some_college_or_associates_degree_F_W = (100 * C15002A_010E)/C15002A_007E,
  Bachelors_degree_or_higher_A_B = (100 * (C15002B_006E + C15002B_011E))/C15002B_001E,
  Bachelors_degree_or_higher_A_W = (100 * (C15002A_006E + C15002A_011E))/C15002A_001E,
  Bachelors_degree_or_higher_M_B = (100 * C15002B_006E)/C15002B_002E,
  Bachelors_degree_or_higher_M_W = (100 * C15002A_006E)/C15002A_002E,
  Bachelors_degree_or_higher_F_B = (100 * C15002B_011E)/C15002B_007E,
  Bachelors_degree_or_higher_F_W = (100 * C15002A_011E)/C15002A_007E,
  ##now for general (non race vars)
  Less_than_high_school_diploma_A_A = (100 * rowSums(across(combined)))/B15002_001E ,
  Less_than_high_school_diploma_M_A = (100 * rowSums(across(lessthanhs_m_vars)))/B15002_002E ,
  Less_than_high_school_diploma_F_A = (100 * rowSums(across(lessthanhs_f_vars)))/B15002_019E ,
  "High_school_graduate_(includes_equivalency)_A_A" = (100 * (B15002_011E + B15002_028E)/B15002_001E),
  "High_school_graduate_(includes_equivalency)_M_A" = (100 * B15002_011E)/B15002_002E,
  "High_school_graduate_(includes_equivalency)_F_A" = (100 * B15002_028E)/B15002_019E,
  Some_college_or_associates_degree_A_A = (100 * (B15002_012E+B15002_013E+B15002_014E +   B15002_029E+B15002_030E+B15002_031E ))/B15002_001E,
  Some_college_or_associates_degree_M_A = (100 * (B15002_012E+B15002_013E+B15002_014E ))/B15002_002E,
  Some_college_or_associates_degree_F_A = (100 * (B15002_029E+B15002_030E+B15002_031E))/B15002_019E,
  Bachelors_degree_or_higher_A_A = (100 * (B15002_015E+B15002_016E+B15002_017E+B15002_018E + B15002_032E+B15002_033E+B15002_034E + B15002_035E))/B15002_001E,
  Bachelors_degree_or_higher_M_A = (100 * (B15002_015E+B15002_016E+B15002_017E+B15002_018E ))/B15002_002E,
  Bachelors_degree_or_higher_F_A = (100 * (B15002_032E+B15002_033E+B15002_034E + B15002_035E ))/B15002_019E
)

allvars <- full_join(allvars, tidyedudf %>% select(matches("_A|_B|_W|GEOID")), by="GEOID")

```

## Health Insurance

```{r}
resultlist <- getdata("B27001", "C27001", TRUE)
tidyhealthdf <- resultlist[[1]]
tidyhealthdf <- tidyhealthdf %>% select("GEOID" | ends_with("E")) %>% select(!"NAME")

##Getting all relevant vars into lists
vars <- resultlist[[2]]

all_m <- (vars %>% filter(str_detect(label, "With"), str_detect(label, "Male"), str_detect(name, "B27001")))$name
all_f <- (vars %>% filter(str_detect(label, "With"), str_detect(label, "Female"), str_detect(name, "B27001")))$name
all_with <- (vars %>% filter(str_detect(label, "With"), str_detect(name, "B27001")))$name
all_b <- (vars %>% filter(str_detect(label, "With"), str_detect(name, "C27001B")))$name
all_w <- (vars %>% filter(str_detect(label, "With"), str_detect(name, "C27001A")))$name

#Add E to the end of everything
f1 <- function(x,y) paste0(x,y)
result <- lapply(list(all_with, all_m, all_f, all_b, all_w), f1, "E")

#above 53 and 56 for all female, 25 and 28 for male
#total 52 and 55 for female, 24 and 27 for male
above_m <- paste0("B27001_0", c(25, 28), "E")
above_f <- paste0("B27001_0", c(53, 56), "E")
above_all <- append(above_m, above_f)
denominatorabove_m <- paste0("B27001_0", c(24, 27), "E")
denominatorabove_f <- paste0("B27001_0", c(52, 55), "E")
denominatorabove_all <- append(denominatorabove_m, denominatorabove_f)

tidyhealthdf <- tidyhealthdf %>% mutate(
  HealthInsurance_A_A = (100*rowSums(across(result[[1]])))/B27001_001E,
  HealthInsurance_M_A = (100*rowSums(across(result[[2]])))/B27001_002E,
  HealthInsurance_F_A = (100*rowSums(across(result[[3]])))/B27001_030E,
  HealthInsurance_A_B = (100*rowSums(across(result[[4]])))/C27001B_001E,
  HealthInsurance_A_W = (100*rowSums(across(result[[5]])))/C27001A_001E,
  SeniorHealthInsurance_A_A = (100*rowSums(across(above_all)))/rowSums(across(denominatorabove_all)),
  SeniorHealthInsurance_M_A =(100*rowSums(across(above_m)))/rowSums(across(denominatorabove_m)),
  SeniorHealthInsurance_F_A = (100*rowSums(across(above_f)))/rowSums(across(denominatorabove_f)),
  #above for white black is 009, total people above for white black is 008
  SeniorHealthInsurance_A_B = (100*C27001B_009E)/C27001B_008E,
  SeniorHealthInsurance_A_W = (100*C27001A_009E)/C27001A_008E
)

allvars <- full_join(allvars, tidyhealthdf %>% select(matches("_A|_B|_W|GEOID")), by="GEOID")

results <- getdata("B27003", raceavailable = FALSE, returnvars = TRUE)
publichealthdf <- results[[1]]
vars <- results[[2]]
vars

#selecting all under 65, with public coverage, and then totals for denominator
all_m <- (vars %>% filter(str_detect(label, "With"), str_detect(label, "Male"), str_detect(name, "B27003")))[1:7,]$name
all_f <- (vars %>% filter(str_detect(label, "With"), str_detect(label, "Female"), str_detect(name, "B27003")))[1:7,]$name
all_with <- append(all_m, all_f)
total_m <- (vars %>% filter(str_detect(label, "Male"),str_detect(label, "Estimate"),str_detect(label, "years"),!str_detect(label,"coverage"),str_detect(name, "B27003")))[1:7,]$name
total_f <- (vars %>% filter(str_detect(label, "Female"),str_detect(label, "Estimate"),str_detect(label, "years"),!str_detect(label,"coverage"),str_detect(name, "B27003")))[1:7,]$name
total <- append(total_m, total_f)
result <- lapply(list(all_with, all_m, all_f, total, total_m, total_f), f1, "E")

publichealthdf <- publichealthdf %>% mutate(
  PublicHealthInsurance_A_A = (100*rowSums(across(result[[1]])))/rowSums(across(result[[4]])),
  PublicHealthInsurance_M_A = (100*rowSums(across(result[[2]])))/rowSums(across(result[[5]])),
  PublicHealthInsurance_F_A = (100*rowSums(across(result[[3]])))/rowSums(across(result[[6]]))
)

allvars <- full_join(allvars, publichealthdf %>% select(matches("_A|_B|_W|GEOID")), by="GEOID")

```

```{r}
rentdf <- getdata("B25064", raceavailable = FALSE)
rentdf <- rentdf %>% rename (
  MedianRent_A_A = B25064_001E
)
allvars <- full_join(allvars, rentdf %>% select(matches("_A|_B|_W|GEOID")), by="GEOID")

housingdf<- getdata("B25003")
housingdf <- housingdf %>% mutate(
  RenterOccupied_A_A = (100*B25003_003E)/B25003_001E,
  RenterOccupied_A_B = (100*B25003B_003E)/B25003B_001E,
  RenterOccupied_A_W = (100*B25003A_003E)/B25003A_001E
)

allvars <- full_join(allvars, housingdf %>% select(matches("_A|_B|_W|GEOID")), by="GEOID")

singlehousingdf <- getdata("S1101", raceavailable = FALSE, subject = TRUE)

##total households S1101_C04_001 and male is S1101_C03_018, female is C04
## so S1101_C04_018* S1101_C04_001 would give total households female single
## and 03 would be male and then could add them up and then divide by sum of total male and female S1101_C04_001
singlehousingdf <- singlehousingdf %>% mutate (
  HH_RenterOccupied_SingleFamily_A_A = 100*((S1101_C03_018E/100* S1101_C03_001E) + (S1101_C04_018E/100* S1101_C04_001E)) / (S1101_C03_001E + S1101_C04_001E),
  HH_RenterOccupied_SingleFamily_M_A = S1101_C03_018E,
  HH_RenterOccupied_SingleFamily_F_A = S1101_C04_018E
)

allvars <- full_join(allvars, singlehousingdf %>% select(matches("_A|_B|_W|GEOID")), by="GEOID")

```

```{r}
car_commutedf <- getdata("B08006", "B08105")
car_commutedf <- car_commutedf %>% mutate (
  Car_truck_van_A_A = (100*B08006_002E)/B08006_001E,
  Car_truck_van_M_A = (100*B08006_020E)/B08006_019E,
  Car_truck_van_F_A = (100*B08006_036E)/B08006_035E,
  Car_truck_van_A_B = (100*B08105B_002E)/B08105B_001E,
  Car_truck_van_A_W = (100*B08105A_002E)/B08105A_001E
)

allvars <- full_join(allvars, car_commutedf %>% select(matches("_A|_B|_W|GEOID")), by="GEOID")

meancommute <- getdata("S0801", raceavailable = FALSE, subject = TRUE)
meancommute <- meancommute %>% mutate (
  Mean_Commute_Time_A_A = S0801_C01_046E
)
allvars <- full_join(allvars, meancommute %>% select(matches("_A|_B|_W|GEOID")), by="GEOID")

results <- getdata("B08012", raceavailable = FALSE, returnvars = TRUE)
commutedf <- results[[1]]
vars <- results[[2]]

lessthan30_all <- paste0("B08012_00", 2:7, "E")
lessthan30_m <- paste0("B08012_0", 15:20, "E")
lessthan30_f <- paste0("B08012_0", 28:33, "E")
range30to60_all <- append(paste0("B08012_00",8:9, "E"),paste0("B08012_0",10:11, "E"))
range30to60_m <- paste0("B08012_0", 21:24, "E")
range30to60_f <- paste0("B08012_0", 34:37, "E")
 
commutedf <- commutedf %>% mutate (
  Less_Than_30_Minutes_A_A = (100*rowSums(across(lessthan30_all)))/B08012_001E,
  Less_Than_30_Minutes_M_A = (100*rowSums(across(lessthan30_m)))/B08012_014E,
  Less_Than_30_Minutes_F_A = (100*rowSums(across(lessthan30_f)))/B08012_027E,
  Range_30_To_60_Minutes_A_A = (100*rowSums(across(range30to60_all)))/B08012_001E,
  Range_30_To_60_Minutes_M_A = (100*rowSums(across(range30to60_m)))/B08012_014E,
  Range_30_To_60_Minutes_F_A = (100*rowSums(across(range30to60_f)))/B08012_027E,
  More_Than_60_Minutes_A_A = (100*(B08012_012E + B08012_013E))/B08012_001E,
  More_Than_60_Minutes_M_A = (100*(B08012_025E + B08012_026E))/B08012_014E,
  More_Than_60_Minutes_F_A = (100*(B08012_038E + B08012_039E))/B08012_027E
)
#commutedf$GEOID<- as.numeric(commutedf$GEOID)
allvars <- full_join(allvars, commutedf %>% select(matches("_A|_B|_W|GEOID")), by="GEOID")


```


##to make sure it doesn't fail on certain vars
```{r}
allvars <- allvars %>% mutate(
FT_Median_Earnings_A_A = 0,
Other_Median_Earnings_A_A = 0
)
```

```{r}
occdf <- getdata("S2401", "C24010", subject = TRUE)

```

```{r}
install.packages("jsonlite")
#library(rjson)

olddata <- read.csv(file = "../MSWomenCount/Data_COMPLETE_cleaned_20210302.csv")
allvars$GEOID <- as.numeric(allvars$GEOID)
combineddata <- full_join(olddata, allvars, by=c("Id2" = "GEOID") )

jsonlite::write_json(combineddata, "../MSWomenCount/src/data/Data_Test_2022_12_23.json")
```


